---
title: "hw1"
output: github_document
---

This is the first homework of data science. 


```{r library_list, include=FALSE}

library(tidyverse)

```


# Problem 1
A random sample of size 10 from a uniform[0, 5] distribution


```{r}

uniform_ten = runif(10,min = 0,max = 5)

```

A logical vector indicating whether elements of the sample are greater than 2

```{r}

def_larger_than_two = ifelse(x > 2 , TRUE, FALSE)

```

A (length-10) character vector

```{r}

char_leng_ten = c("a" , "b" , "c" , "e" , "f", "g", "h", "i", "j", "k")
length(char_leng_ten)

```

A (length-10) factor vector

```{r}

fac_leng_ten = factor(c("a" , "b" , "c" , "e" , "f", "g", "h", "i", "j", "k"))
length(fac_leng_ten)

```

Create a dataframe of these vectors
```{r}
data_frame_q1 = data.frame(uniform_ten,def_larger_than_two,char_leng_ten,fac_leng_ten)
```

# Section 2

Create a dataframe of four vectors:

```{r}
set.seed(1)
x = rnorm(1000)

y = rnorm(1000)

log_flag = ifelse(x + y > 0, TRUE, FALSE)

num_flag = as.numeric(log_flag)

fac_flag = as.factor(log_flag)

data_frame_q2 = data.frame(x,y,log_flag,num_flag,fac_flag)
str(data_frame_q2)

```

This is a brief introduction of this dataset:

The size of the dataset is `r ncol(data_frame_q2)` colums and `r nrow(data_frame_q2)` rows.

The mean of x is `r mean(x)` and median is `r median(x)`.

```{r include=FALSE}
######
#cnt = 0
#while (cnt < ncol(data_frame_q2)) {
#   print(cnt)
#   cnt = cnt + 1
#}
######

x_def = ifelse(class(x) == 'logical', 1, 0)
y_def = ifelse(class(y) == 'logical', 1, 0)
log_def = ifelse(class(log_flag) == 'logical', 1, 0)
num_def = ifelse(class(num_flag) == 'logical', 1, 0)
fac_def = ifelse(class(fac_flag) == 'logical', 1, 0)
sum = x_def + y_def + log_def + num_def + fac_def

```
  
The proportion of cases for which the logical vector is `r sum/ncol(data_frame_q2)` 


